What's in a name? On the automated topic naming of software maintenance activities

### 2010-03-05 icpc/icpc2010.tex
Add MSR reference

Unlike the poetic license Shakespeare uses, we show that names are indeed important. The rose has its own tangible properties which allow us to sense it. Unfortunately when we are dealing with data abstracted from program source code, we are already dealing with abstract entities that are not tangible.

During the development of a software project developers touch on many issues integral to the purpose of the software project. These issues are often referred to as topics. These topics can sometimes be automatically extracted from the changelog comments that developers create while committing revisions to the project's source control repository. Our previous work dealt with topic-trends~\cite{Hindle09ICSM}, topics that repeat overtime. It seemed that these trends were often non-functional requirements.

@@

 Binary Relevance (BR), Calibrated Label Ranking (CLR) and Hierarchy Of Multilabel classifiERs (HOMER), performed the best. HOMER and BR acts as a hierarchy of learners, BR is flat while HOMER tries to build a deeper hierarchy in order to build a more accurate learner~\cite{mulan}. We feels these classifiers performed better because they have the best micro and macro ROC scores than the other classifiers.

\XXX{finish this}
\XXX{Clean up tables with labels}
\begin{table*}
\centering
\begin{tabular}{l|rrrrrrrr}

@@

We observed that MySQL had more topic subsets than MaxDB.

* we had more MySQL recorded
* both shared functionality maintainability and portability

@@

The idea of extracting higher-level `concerns' (also known as `concepts', `aspects' or `requirements') has been attacked in two ways.

>>>>

As development of a software project progresses, developers must concern themselves with a wide variety of issues --- or ``topics'' --- that relate to the problem domain, the processes and tools used, the development artifacts themselves, etc.  The set of development topics for a given project can sometimes be extracted automatically by analyzing artifacts within software repositories, such as changelog comments that developers create when committing revisions to the project's source control system.  Our previous work dealt with topic trends, which are topics that recur over time~\cite{Hindle09ICSM}. We observed that topic trends were often non-functional requirements.

%During the development of a software project developers touch on many %issues integral to the purpose of the software project. These issues %are often referred to as topics. These topics can sometimes be %automatically extracted from the changelog comments that developers %create while committing revisions to the project's source control %repository. Our previous work dealt with %topic-trends~\cite{Hindle09ICSM}, topics that repeat overtime. It %seemed that these trends were often non-functional requirements.

@@

Binary Relevance (BR), Calibrated Label Ranking (CLR) and Hierarchy Of Multilabel classifiERs (HOMER), performed the best. HOMER and BR acts as a hierarchy of learners, BR is flat while HOMER tries to build a deeper hierarchy in order to build a more accurate learner~\cite{mulan}. We feel that these classifiers performed better because they have the best micro and macro ROC scores than the other classifiers.

\begin{table*}
\centering
\begin{tabular}{l|rrrrrrrr}

@@

We observed that MySQL had more topic subsets than MaxDB. MySQL 3.23 also had more topics and a longer recorded history than MaxDB 7.500. We tagged more MySQL topics with annotations than MaxDB topics yet both shared similarities. In terms of non-functional requirements both projects had long running trends that focused on functionality, maintainability, and portability, yet MaxDB had more of a focus on efficiency and reliability. We feel that MaxDB differed from MySQL because MaxDB was being actively developed where was by half way through our history of MySQL 3.23, other versions of MySQL were being actively developed: MySQL versions 4.0 and 4.1 and eventually 5.0 and 5.1. MySQL 3.23 was being maintained rather than actively developed where as MaxDB 7.500 was being actively developed into MaxDB 7.6, and then maintained thereafter.

@@

% Not sure how do handle this
The idea of extracting higher-level `concerns' (also known as `concepts', `aspects' or `requirements') has been attacked in two ways.
